Probabilistic Forecasts in Hierarchical Time Series

### 2018-01-09 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

\noindent
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$\\

@@

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
&\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
\end{flalign*}
\noindent
Recall that, $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
\end{pmatrix} = \begin{pmatrix}
\bm{P}\\\bm{Q}
\end{pmatrix},$(say). Then,

@@

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
	\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
	\end{pmatrix}\Big|^{\frac{1}{2}}}
\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T\\ 
&\Big[\begin{pmatrix}
\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
\end{pmatrix}\Big]^{-1} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
\end{flalign*}
\noindent
$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, which is a multivariate Gaussian distribution. Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,

\begin{flalign}\label{ex:2.1}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}
\end{flalign}

\noindent
(\ref{ex:2.1} ) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$. Then from (\ref{4.7}) it follows that

\begin{flalign}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{flalign}
\noindent
That is the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.

@@

\noindent
Calibration refers to the statistical compatibility between probabilistic forecasts and realizations. In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations. The uniformity in Probability Integral Transformation (PIT) of predictive densities evaluated at realizations implies well calibrated probabilistic forecasts. Therefore, assessing the uniformity in PIT of predictive densities, by inspecting their histograms and correlograms can be used as a simple tool for evaluating the calibration of probabilistic forecasts.  \\

\noindent
On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only. The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}. The sharpness of density forecasts can be assessed in terms of the prediction intervals. Sharper density forecasts will have shorter prediction intervals. However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts. Therefore to assess these properties simultaneously, we use scoring rules. \\

@@

\noindent
Let $\bm{Y}$ be a $n$-dimensional random vector from the predictive distribution $\mathbold{F}$ and $\mathbold{y}$ be $n$-dimension vector of realizations. Scoring rule is a numerical value $S(\mathbold{Y,y})$ assign to each pair $(\mathbold{Y,y})$. Suppose the true distribution of $\mathbold{y}$ is given by $\mathbold{G}$. Then the proper scoring rule is defined as,
\begin{equation}\label{eq:(3.1.)}
S(\mathbold{G,G}) \le S(\mathbold{Y,G}),
\end{equation}
\noindent
where $S(\mathbold{Y,G})=E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\

\noindent
Let $\bm{\tilde{Y}}_{T+h}$ and $\bm{\tilde{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\tilde{\bm{F}}$ with the density function $\tilde{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\tilde{Y}_{T+h,i}$ and $\tilde{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\tilde{\bm{Y}}_{T+h}$. Then the following table summarizes few existing proper scoring rules.

@@

	\resizebox{\linewidth}{!}{

		\begin{tabular}{ L | L | L}
			\hline
			\hline
			\textbf{Scoring rule} & \textbf{Expression} & \textbf{Reference}\\
			\\
			\hline
			\hline \\
			\text{Log score} & LS(\tilde{\bm{F}},\bm{y}_{T+h}) = -log {\tilde{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
			\\ 
			\hline \\
			\text{Energy score} & eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\tilde{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
			\\
			\hline
			\text{Variogram score} & VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\tilde{\bm{F}}}|\tilde{Y}_{T+h,i}-\tilde{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
			\hline
		\end{tabular}

		}
\end{center}

\noindent
Log scores can be used to evaluate the hierarchical probabilistic forecasts if it is reasonable to assume a parametric forecast density for the hierarchy. However the \qq{degenerecy} of the coherent forecast densities would be problematic when using log scores. We will discuss more about this in the next sub section.\\

\noindent
In the energy score, for $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\tilde{\bm{\mu}}_{T+h}||^2,
\end{equation}

\noindent
where $\tilde{\bm{\mu}}_{T+h} =E_{\bm{F}}(\tilde{\bm{Y}}_{T+h}) $. Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution. Further \citet{Pinson2013a} argued that the Energy score given in table 1 has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well. \\

\noindent
The variogram score given in Table $1$ is for order $p$ where, $w_{ij}$ are non-negative weights. \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score. Further they suggested the variogram score with $p=0.5$ is more powerful.\\

\noindent
For a possible finite sample of size $B$ from the multivariate forecast density $\tilde{\bm{F}}$, the variogram score is defined as,

\begin{flalign}
VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\tilde{Y}^k_{T+h,i}-\tilde{Y}^k_{T+h,j}|^p\right)^2.
\end{flalign}

@@

As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule that has been introduced in literature to evaluate densities with degeneracy. Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy. For example take the log score in the univariate case. Suppose the true density is degenerate at $x=0$, i.e. $f(x)=\mathbb{1}\{x=0\}$.  Now consider two predictive densities $p_1(x)$ and $p_2(x)$. Let $p_1(x)$ is equivalent to the true density, i.e. $p_1(x)=\mathbb{1}\{x=0\}$ and $p_2(x) =^d N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$. The expected log score of $p_1$ is:
$$S(f,f) = S(p_1,f) -ln[p_1(x=0)]=0,$$
\noindent
and that of $p_2$ is:
$$S(p_2,f) = -ln[p_2(x=0)]<0.$$ 
\noindent
Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition (\ref{eq:(3.1.)}) for proper scoring rule. This implies log score cannot be used to evaluate the degenerate densities.  \\

@@

\noindent
However you could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this. \\

\begin{equation} \label{eq:(3.6)}
CRPS(\tilde{F}_i,y_{T+h,i}) = E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-\tilde{Y}'_{T+h,i}|,
\end{equation}

\noindent
where $\tilde{Y}_{T+h,i}$ and $\tilde{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.

>>>>

\noindent
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$. Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.\\

@@

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
&\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
\end{flalign*}
\noindent
Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
\end{pmatrix} = \begin{pmatrix}
\bm{P}\\\bm{Q}
\end{pmatrix},$$ where, $\bm{P}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$ and $\bm{Q}=(\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot$. Then,

@@

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
	\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
	\end{pmatrix}\Big|^{\frac{1}{2}}}
\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T\\ 
&\Big[\begin{pmatrix}
\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
\end{pmatrix}\Big]^{-1} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
\end{flalign*}
\noindent
$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, which is a multivariate Gaussian distribution. Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,
\begin{flalign}\label{ex:2.1}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
\end{flalign}

\noindent
(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$. Then from (\ref{4.7}) it follows that,
\begin{flalign}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{flalign}
\noindent
Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.

@@

\noindent
Calibration refers to the statistical compatibility between probabilistic forecasts and realizations. In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations. On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only. The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}. However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts. Therefore to assess these properties simultaneously, we use scoring rules. \\

@@

\noindent
Let $\bm{{\breve{Y}}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\mathbold{F}$ and the true distribution $\mathbold{G}$. Further let $\mathbold{y}$ be a $n$-dimensional realization. Then the scoring rule is a numerical value $S(\mathbold{{\breve{Y}},y})$ assign to each pair $(\mathbold{{\breve{Y}},y})$ and the proper scoring rule is defined as,
\begin{equation}\label{eq:(3.1.)}
E_{\mathbold{G}}[S(\mathbold{Y,y})] \le E_{\mathbold{G}}[S(\mathbold{{\breve{Y}},y})],
\end{equation}
\noindent
where $E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\

\noindent
Following table summarizes few existing proper scoring rules.

@@

	\small
	\resizebox{\linewidth}{!}{

		\begin{tabular}{ L | L | L}
			\hline
			\hline
			\textbf{Scoring rule} & \textbf{Expression} & \textbf{Reference}\\
			\\
			\hline
			\hline \\
			\text{Log score} & LS(\breve{\bm{F}},\bm{y}_{T+h}) = -log {\breve{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
			\\ 
			\hline \\
			\text{Energy score} & eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
			\\
			\hline
			\text{Variogram score} & VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
			\hline
		\end{tabular}

		}
\end{center}
\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$. Further the variogram score given is for order $p$ where, $w_{ij}$ are non-negative weights.}\\

\noindent
Even though the log score can be used evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if it is reasonable to assume a parametric forecast density for the hierarchy. However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores. We will discuss more about this in the next sub section.\\

\noindent
In the energy score, for $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}||^2,
\end{equation}

\noindent
where $\breve{\bm{\mu}}_{T+h} =E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution. Further \citet{Pinson2013a} argued that the Energy score given in table 1 has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well. \\

\noindent
However, \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score. Further they suggested the variogram score with $p=0.5$ is more powerful.\\
\noindent
For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,

\begin{flalign}
VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
\end{flalign}

@@

As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule in literature to evaluate degenerate densities. Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy. For example take the log score in the univariate case. Suppose the true density is degenerate at $x=0$, i.e. $f(x)=\mathbb{1}\{x=0\}$.  Now consider two predictive densities $p_1(x)$ and $p_2(x)$. Let $p_1(x)$ is equivalent to the true density, i.e. $p_1(x)=\mathbb{1}\{x=0\}$ and $p_2(x) =^d N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$. The expected log score of $p_1$ is:
$$E_f[S(f,f)] = E_f[S(p_1,f)] = -ln[p_1(x=0)]=0,$$
\noindent
and that of $p_2$ is:
$$E_f[S(p_2,f)] = -ln[p_2(x=0)]<0.$$ 
\noindent
Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition (\ref{eq:(3.1.)}) for proper scoring rule. This implies log score cannot be used to evaluate the degenerate densities.  \\

@@

\noindent
However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this. \\

\begin{equation} \label{eq:(3.6)}
CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}'_{T+h,i}|,
\end{equation}

\noindent
where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
